---
title: "ML Output Kenya"
author: "Fiona Spooner"
date: "July 23, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.width = 12, fig.height = 9)
```


```{r}
library(here)
library(dplyr)
library(ggplot2)
library(stringr)
library(reshape2)
library(purrr)
library(readr)
library(scales)

```

#Effort

Calculating the daily effort at each site i.e. the number of cameras that were on each day at each site

```{r, eval = FALSE}

mn<-read.csv(here::here("effort/naboisho_effort.csv"), stringsAsFactors = FALSE, na.strings=c("","NA"))
mn$Start_1<-as.Date(mn$Start_1, format = "%d-%m-%y") 
mn$End_1<-as.Date(mn$End_1, format = "%d-%m-%y") 

mn$Start_2<-as.Date(mn$Start_2, format = "%d-%m-%y")
mn$End_2<-as.Date(mn$End_2, format = "%d-%m-%y")

start<-min(na.omit(mn$Start_1))
end<-max(na.omit(mn$End_2))

all_days<-seq(start, end, by = "day")
all_zeros<-rep(0, length(all_days))

effort_func<-function(loc){
  
  site<-mn[mn$Location_ID == loc,]
  effort<-all_zeros

  if(!is.na(site$Start_1) & !is.na(site$End_1)){
    loc_start1<-site$Start_1
    loc_end1<-site$End_1
    effort[which(all_days == loc_start1):which(all_days == loc_end1)]<-1
  }

  if(!is.na(site$Start_2) & !is.na(site$End_2)){
    loc_start2<-site$Start_2
    loc_end2<-site$End_2
    effort[which(all_days == loc_start2):which(all_days == loc_end2)]<-1
  }  
  print(loc)
  return(effort)
  
  }


effort_out<-lapply(mn$Location_ID,effort_func)

effort_mat<-do.call("rbind", effort_out)

effort_sum<-colSums(effort_mat)

plot(effort_sum, type = "l")

effort_df<-data.frame(mn$Location_ID,effort_mat)
colnames(effort_df)<-c("Location_ID", as.character(all_days))

#write.csv(effort_df, here::here("effort/naboisho_effort_matrix.csv"), row.names = FALSE)


```

####Combining the effort matrices

```{r, eval = FALSE}

effort_files<-list.files(here::here("/effort"),pattern = "*_effort_matrix.csv")

eff<-read.csv(effort_files[4])

eff_sum<-melt(colSums(eff[,2:ncol(eff)]))
eff_sum$date<-as.Date(row.names(eff_sum), format = "X%Y.%m.%d")
eff_sum$site<-"OMC"

#write.csv(eff_sum, here::here("/effort/omc_daily_effort.csv"), row.names = FALSE)


```

```{r, eval = FALSE}

files <- list.files(here::here("effort"),pattern = "*daily_effort.csv", full.names = TRUE)

ef <- files %>%
  map(read_csv) %>%    # read in all the files individually, using
  reduce(rbind)        # reduce with rbind into one dataframe

colnames(ef)[1]<-"effort"

#write.csv(ef,here::here("effort/all_sites_effort.csv"), row.names = FALSE)

```


####Animal vs No Animal

Producing figures to show the total number of images at each site categorised as either Animal or no Animal

```{r,eval = FALSE}

lf<-list.files(here::here("/results_csvs/phase1"), pattern = "*_results.csv", full.names =  TRUE)

filer<-function(file){
  
  file_in<-read.csv(file, header = FALSE)
  file_in$filename<-basename(file)
  return(file_in)  
}

files_out<-lapply(lf, filer)

allp1<-do.call("rbind", files_out)

write.csv(allp1, here::here("results_csvs/phase1/all_sites_seasons.csv"), row.names = FALSE)


```


```{r, eval = FALSE}

allp1<-read.csv(here::here("results_csvs/phase1/all_sites_seasons.csv"), stringsAsFactors = FALSE)
colnames(allp1)<-c("row_no", "IMG_ID","unsure", "Animal", "NoAnimal", "ConfAnim", "ConfNoAnim", "SiteSeason")


```

Formatting the ML output

```{r, eval = FALSE}

allp1$Site<-allp1$SiteSeason%>%
              gsub("_november_results.csv", "", .)%>%
              gsub("_october_results.csv", "", .)%>%
              gsub("_november_repaired_results.csv", "", .)%>%
              gsub("_october_repaired_results.csv", "", .)

allp1$Season<-allp1$SiteSeason%>%
              gsub("_results.csv", "", .)%>%
              gsub("_repaired", "", .)%>%
              gsub("mara_north_", "", .)%>%
              gsub("mara_triangle_", "", .)%>%
              gsub("naboisho_", "", .)%>%
              gsub("omc_", "", .)

#getting rid of the summary rows at the end of each data sheet

alldf<-allp1[-which(allp1$Animal != "[0" & allp1$Animal != "[1"),]


alldf$Animal[alldf$Animal == "[0"]<-0
alldf$Animal[alldf$Animal == "[1"]<-1

alldf$ConfAnim<-gsub("\\[","", alldf$ConfAnim)

alldf$IMG_ID_nospl<-alldf$IMG_ID%>%
                      gsub("_0.JPG","", .)%>%
                      gsub("_1.JPG","", .)

```

Merging the split images together by summing the animal column. Anything with a 1 or 2 will be recoded as 1, and 0 will remain 0.

```{r, eval = FALSE, echo = FALSE}

alldf$Animal<-as.numeric(alldf$Animal)
alldf$ConfAnim<-as.numeric(alldf$ConfAnim)

alldf$ID_unique<-paste(alldf$Site, alldf$Season, alldf$IMG_ID_nospl, sep = "/")

alldf<-alldf %>%
  group_by(ID_unique)%>%
  mutate(SumAnimal = sum(Animal), MeanConf = mean(ConfAnim))

alldf$Camera<-dirname(alldf$IMG_ID)


df<-alldf%>%
  dplyr::select(ID_unique, Site,Camera ,Season,  SumAnimal, MeanConf)%>%
  distinct() %>%
  ungroup()

df$SumAnimal[df$SumAnimal == 2]<-1

df$SumAnimalF<-as.factor(df$SumAnimal)

cam_split<-strsplit(df$Camera, "/")

get_first<-function(x){
  image_out<-x[[1]]
  return(image_out)
  }

cam_out<-lapply( cam_split,get_first)

df$CamUnique<-unlist(cam_out)


```

```{r, eval = FALSE, echo =FALSE}

camsum<-df %>%
  group_by(CamUnique,SumAnimalF)%>%
  #filter(MeanConf >= 0.9)%>%
  summarise(Freq = n())

#write.csv(camsum, "Camera_Animal_No_Animal.csv", row.names = FALSE)

```

```{r, eval = FALSE, echo = FALSE}

df_tot<-df
df_tot$Site<-"Total"

df_all<-rbind(df, df_tot)
df_all$Site<-as.factor(df_all$Site)

#write.csv(df_all, "Kenya_Animal_No_Animal.csv", row.names = FALSE)
```

```{r, echo = FALSE}

df_all<-read.csv("Kenya_Animal_No_Animal.csv", stringsAsFactors = FALSE)

df_all$Site_f<-as.factor(df_all$Site)
df_all$Site_f<-factor(df_all$Site_f, levels(df_all$Site_f)[c(5,2,4,3,1)])

df_all$SumAnimalF<-as.factor(df_all$SumAnimalF)

site_labs<- c("Total", "Mara North", "Mara Triangle", "Naboisho", "OMC")
names(site_labs)<-c("Total", "mara_north", "mara_triangle", "naboisho", "omc")


df_all$SiteCode<-df_all$Site
df_all$SiteCode[df_all$SiteCode == "mara_north"]<-"MN"
df_all$SiteCode[df_all$SiteCode == "mara_triangle"]<-"MT"
df_all$SiteCode[df_all$SiteCode == "naboisho"]<-"NB"
df_all$SiteCode[df_all$SiteCode == "omc"]<-"OMC"

```

```{r}
ggplot(df_all, aes(SumAnimalF, fill = SumAnimalF))+
  geom_bar()+
  facet_wrap(.~Site_f, labeller = labeller(Site_f = site_labs))+
  labs(x = "", y = "Number of Images")+
  scale_x_discrete(labels=c("0" = "No Animal", "1" = "Animal"))+
  scale_y_continuous(labels = comma)+
  scale_fill_manual( values = c("0" = "black", "1" = "grey"))+ 
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.position = "none",
        strip.text.x = element_text(size = 14))


```

```{r}

sitesum<-df_all %>%
  group_by(Site_f,SumAnimalF,  SiteCode)%>%
  #filter(MeanConf >= 0.9)%>%
  summarise(Freq = n())

sitesum$SumAnimalF<-as.factor(sitesum$SumAnimalF)
sitesum$SumAnimalF<-factor(sitesum$SumAnimalF, levels(sitesum$SumAnimalF)[c(2,1)])


ggplot(sitesum, aes(x =Site_f ,y = Freq ,alpha = SumAnimalF, fill = Site_f))+
  geom_bar(position="dodge", stat="identity")+
  labs(x = "", y = "Number of Images", fill ="", alpha = "")+
  scale_alpha_discrete(range = c(1, 0.35), labels = c("Animal", "No Animal"))+
  scale_x_discrete(labels=c("mara_north" = "Mara North", "mara_triangle" = "Mara Triangle", "naboisho" = "Naboisho", "omc" = "OMC"))+
  guides(fill = FALSE)+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  #scale_fill_manual(values = c("0" = "black", "1" = "grey"), labels = c("No Animal", "Animal"))+ 
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 18))


#write.csv(sitesum, "Kenya_Animal_No_Animal_Summary.csv", row.names = FALSE)

```

###Image counts with effort accounted for

```{r}
ef<-read.csv(here::here("effort/all_sites_effort.csv"), stringsAsFactors = FALSE)

ef_sum <-ef %>%
  group_by(site)%>%
  summarise(sum_ef = sum(effort))

ef_tot<-data.frame("Total",sum(ef$effort) )
colnames(ef_tot)<-colnames(ef_sum)

ef_all<-rbind(ef_tot, ef_sum)

```

```{r, echo = FALSE}

site_ef<-merge(ef_all, sitesum, by.x = "site", by.y = "SiteCode")

site_ef$FreqEff<-site_ef$Freq/site_ef$sum_ef


```

```{r}

ggplot(site_ef, aes(x =Site_f ,y = FreqEff ,alpha = SumAnimalF, fill = Site_f))+
  geom_bar(position="dodge", stat="identity")+
  labs(x = "", y = "Number of Images per Camera Trap Day", fill ="", alpha = "")+
  scale_alpha_discrete(range = c(1, 0.35), labels = c("Animal", "No Animal"))+
  scale_x_discrete(labels=c("mara_north" = "Mara North", "mara_triangle" = "Mara Triangle", "naboisho" = "Naboisho", "omc" = "OMC"))+
    scale_y_continuous(labels = comma)+
  guides(fill = FALSE)+
  theme_bw()+
  #scale_fill_manual(values = c("0" = "black", "1" = "grey"), labels = c("No Animal", "Animal"))+ 
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 18))

```


##Excluding images below 90% Confidence Threshold

```{r, echo = FALSE}

sitesum<-df_all %>%
  group_by(Site_f,SumAnimalF,  SiteCode)%>%
  filter(MeanConf >= 0.9)%>%
  summarise(Freq = n())

sitesum$SumAnimalF<-as.factor(sitesum$SumAnimalF)
sitesum$SumAnimalF<-factor(sitesum$SumAnimalF, levels(sitesum$SumAnimalF)[c(2,1)])

site_ef<-merge(ef_all, sitesum, by.x = "site", by.y = "SiteCode")

site_ef$FreqEff<-site_ef$Freq/site_ef$sum_ef

```

####90% Confidence Threshold *not* accounting for effort

```{r, echo = FALSE}
sitesum<-df_all %>%
  group_by(Site_f,SumAnimalF,  SiteCode)%>%
  filter(MeanConf >= 0.9)%>%
  summarise(Freq = n())

sitesum$SumAnimalF<-as.factor(sitesum$SumAnimalF)
sitesum$SumAnimalF<-factor(sitesum$SumAnimalF, levels(sitesum$SumAnimalF)[c(2,1)])


ggplot(sitesum, aes(x =Site_f ,y = Freq ,alpha = SumAnimalF, fill = Site_f))+
  geom_bar(position="dodge", stat="identity")+
  labs(x = "", y = "Number of Images", fill ="", alpha = "")+
  scale_alpha_discrete(range = c(1, 0.35), labels = c("Animal", "No Animal"))+
  scale_x_discrete(labels=c("mara_north" = "Mara North", "mara_triangle" = "Mara Triangle", "naboisho" = "Naboisho", "omc" = "OMC"))+
  scale_y_continuous(labels = comma)+
  guides(fill = FALSE)+
  theme_bw()+
  #scale_fill_manual(values = c("0" = "black", "1" = "grey"), labels = c("No Animal", "Animal"))+ 
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 18))

```

####90% Confidence Threshold accounting for effort

```{r}

ggplot(site_ef, aes(x =Site_f ,y = FreqEff ,alpha = SumAnimalF, fill = Site_f))+
  geom_bar(position="dodge", stat="identity")+
  labs(x = "", y = "Number of Images\n per Camera Trap Day", fill ="", alpha = "")+
  scale_alpha_discrete(range = c(1, 0.35), labels = c("Animal", "No Animal"))+
  scale_x_discrete(labels=c("mara_north" = "Mara North", "mara_triangle" = "Mara Triangle", "naboisho" = "Naboisho", "omc" = "OMC"))+
  scale_y_continuous(labels = comma)+
  guides(fill = FALSE)+
  theme_bw()+
  #scale_fill_manual(values = c("0" = "black", "1" = "grey"), labels = c("No Animal", "Animal"))+ 
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 14),
        strip.text.x = element_text(size = 14))



```





###Species Counts

```{r, eval = FALSE, echo = FALSE}
lf<-list.files(here::here("/results_csvs/phase2"), pattern = "*_results.csv",full.names =  TRUE)

filer<-function(file){
  
  file_in<-read.csv(file, header = FALSE)
  file_in$filename<-basename(file)
  return(file_in)  
}

files_out<-lapply(lf, filer)

allp2<-do.call("rbind", files_out)

#write.csv(allp2, here::here("results_csvs/phase2/all_sites_seasons.csv"), row.names = FALSE)

```

```{r}
allp2<-read.csv(here::here("results_csvs/phase2/all_sites_seasons.csv"), stringsAsFactors = FALSE)

allp2<-dplyr::select(allp2, "V2", "V11", "V16", "filename")
colnames(allp2)<-c("IMG_ID", "Species_Code", "Confidence", "Filename")

```

```{r}
species_id<-read.csv("species_codes.csv", header = FALSE)
colnames(species_id)<-c("CommonName", "Code")

```

```{r}

allp2$Species_Code<-gsub("\\[", "", allp2$Species_Code)
allp2$Confidence<-gsub("\\[", "", allp2$Confidence)


allp2$Site<-allp2$Filename%>%
              gsub("_november_phase2ready_phase2_results.csv", "", .)%>%
              gsub("_october_phase2ready_phase2_results.csv", "", .)%>%
              gsub("_november_repaired_phase2ready_phase2_results.csv", "", .)%>%
              gsub("_october_repaired_phase2ready_phase2_results.csv", "", .)

allp2$Season<-allp2$Filename%>%
              gsub("_phase2ready_phase2_results.csv", "", .)%>%
              gsub("_repaired", "", .)%>%
              gsub("mara_north_", "", .)%>%
              gsub("mara_triangle_", "", .)%>%
              gsub("naboisho_", "", .)%>%
              gsub("omc_", "", .)

allp2$IMG_ID<-as.character(allp2$IMG_ID)

cam_split<-strsplit(allp2$IMG_ID, "/")

get_first<-function(x){
  image_out<-x[[1]]
  return(image_out)
  }

cam_out<-lapply(cam_split,get_first)

allp2$CamUnique<-unlist(cam_out)


```

```{r, echo = FALSE}

allsp<-merge(allp2, species_id, by.x = "Species_Code", by.y = "Code")

allsp$ID_unique<-paste(allsp$Site, allsp$Season, allsp$IMG_ID, sep = "/")

allsp$ID_unique<-allsp$ID_unique%>%
                    gsub("_0.JPG", "", .)%>%
                    gsub("_1.JPG", "", .)

allsp$Confidence<-as.numeric(allsp$Confidence)

allsp<-allsp %>%
          group_by(ID_unique)%>%
          mutate(MeanConf = mean(Confidence))%>%
          ungroup()
      
df<-allsp%>%
  dplyr::select(ID_unique, Species_Code, Site, CamUnique, Season,  CommonName, MeanConf)%>%
  distinct()%>%
  group_by(CommonName)%>%
  #filter(MeanConf >= 0.9)%>%
  mutate(FreqCommonName = n())%>%
  arrange(-FreqCommonName)


```


Joining the ML output with the exif data to join the species data with a date


```{r, echo = FALSE, eval = FALSE}

df$CommonName<-str_trim(df$CommonName)

ggplot(df, aes(CommonName))+
  geom_bar()+
  labs(x = "", y = "Number of Images", fill = "")+
  scale_y_continuous(labels = comma)+
   scale_x_discrete(limits=c("Wildebeest", "Other Bird", "Zebra", "Human", "Guineafowl", "Gazelle Thomsons", "Warthog", "Elephant", "Giraffe", "Impala", "Gazelle Grants", "Buffalo", "Eland", "Mongoose", "Hyena Spotted", "Vervet Monkey", "Baboon", "Hartebeest", "Reedbuck", "Hare", "Topi", "Lion Female", "Dikdik", "Hippopotamus", "Koribustard", "Jackal", "Secretary Bird", "Cheetah", "Bateared Fox", "Ostrich", "Serval", "Porcupine", "Waterbuck", "Lion Male", "Leopard", "Aardvark", "Rodents", "Caracal", "Bushbuck", "Aardwolf", "Hyena Striped", "Reptiles", "Civet", "Wild Cat"))+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 13,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 14),
        strip.text.x = element_text(size = 14))


```

##90% confidence

```{r, echo = FALSE, eval = FALSE}

df_filt<-df%>%
  filter(MeanConf >=0.9)%>%
  group_by(CommonName)%>%
  mutate(freq = n())%>%
  ungroup()%>%
  arrange(desc(freq))

ggplot(df_filt, aes(CommonName))+
  geom_bar()+
  labs(x = "", y = "Number of Images", fill = "")+
  scale_x_discrete(limits=c(unique(df_filt$CommonName)))+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 13,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 14),
        strip.text.x = element_text(size = 14))


```


```{r}
dfs<-allsp%>%
  dplyr::select(ID_unique, Species_Code, Site, CamUnique, Season,  CommonName, MeanConf)%>%
  distinct()%>%
  group_by(CommonName,Site)%>%
  #filter(MeanConf >= 0.9)%>%
  mutate(FreqCommonName = n())%>%
  arrange(-FreqCommonName)

dfs$site_code <- dfs$Site

dfs$site_code[dfs$site_code == "naboisho"]<-"NB"
dfs$site_code[dfs$site_code == "mara_north"]<-"MN"
dfs$site_code[dfs$site_code == "mara_triangle"]<-"MT"
dfs$site_code[dfs$site_code == "omc"]<-"OMC"

```

```{r, echo = FALSE}

ef<-read.csv(here::here("effort/all_sites_effort.csv"))

ef_site<- ef %>%
          group_by(site)%>%
          summarise(total_effort = sum(effort))%>%
          ungroup()



```

```{r, echo = FALSE}

dfe<-merge(dfs, ef_site, by.x = "site_code", by.y = "site")
dfe$CommonName<-as.character(dfe$CommonName)

# df_tot<-dfe%>%
#   group_by(CommonName)%>%
#   mutate(sum_freq = sum(as.numeric(FreqCommonName)), sum_effort = sum(as.numeric(total_effort)), FreqEffort = sum_freq/sum_effort)%>%
#   select(CommonName, sum_freq,sum_effort,FreqEffort, MeanConf)%>%
#   ungroup()

df_tot<-dfe
df_tot$site_code <-"Total"

#dfe$FreqEffort<-dfe$FreqCommonName/dfe$total_effort
# 
# dfef<-dfe %>%
#   dplyr::select(CommonName,FreqEffort,site_code, MeanConf)%>%
#   distinct()

df_all<-rbind(df_tot, dfe)

```

```{r}
gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

cols = gg_color_hue(5)
site_code = c("Total", "MT", "OMC", "NB", "MN")

site_cols<-data.frame(cols, site_code)

df_col<-merge(df_all, site_cols, by = "site_code")


df_col$CommonName<-str_trim(df_col$CommonName)

```
#Total

```{r, echo = FALSE}

df_tot<-df_col%>%
  filter(site_code == "Total")%>%
  group_by(CommonName)%>%
  mutate(freq = n())%>%
  ungroup()%>%
  arrange(desc(freq))


ggplot(df_tot, aes(x = CommonName))+
  geom_bar(fill = df_tot$cols[1])+
  labs(x = "", y = "Number of Images", fill = "")+
  scale_x_discrete(limits=c(unique(df_tot$CommonName)))+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 15,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 18))


```

##Total, Confidence >= 90%

```{r, echo = FALSE}

df_tot<-df_col%>%
  filter(MeanConf >=0.90,site_code == "Total")%>%
  group_by(CommonName)%>%
  mutate(freq = n())%>%
  ungroup()%>%
  arrange(desc(freq))


ggplot(df_tot, aes(x = CommonName))+
  geom_bar(fill = df_tot$cols[1])+
  labs(x = "", y = "Number of Images", fill = "")+
  scale_x_discrete(limits=c(unique(df_tot$CommonName)))+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 15,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 18))


```

##Mara North

```{r, echo = FALSE}

df_tot<-df_col%>%
  filter(site_code == "MN")%>%
  group_by(CommonName)%>%
  mutate(freq = n())%>%
  ungroup()%>%
  arrange(desc(freq))


ggplot(df_tot, aes(x = CommonName))+
  geom_bar(fill = df_tot$cols[1])+
  labs(x = "", y = "Number of Images", fill = "")+
  scale_x_discrete(limits=c(unique(df_tot$CommonName)))+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 15,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 18))


```

##Mara North Confidence >= 90%


```{r, echo = FALSE}

df_tot<-df_col%>%
  filter(MeanConf >=0.90,site_code == "MN")%>%
  group_by(CommonName)%>%
  mutate(freq = n())%>%
  ungroup()%>%
  arrange(desc(freq))


ggplot(df_tot, aes(x = CommonName))+
  geom_bar(fill = df_tot$cols[1])+
  labs(x = "", y = "Number of Images", fill = "")+
  scale_x_discrete(limits=c(unique(df_tot$CommonName)))+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 15,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 18))


```

##Mara Triangle

```{r, echo = FALSE}

df_tot<-df_col%>%
  filter(site_code == "MT")%>%
  group_by(CommonName)%>%
  mutate(freq = n())%>%
  ungroup()%>%
  arrange(desc(freq))


ggplot(df_tot, aes(x = CommonName))+
  geom_bar(fill = df_tot$cols[1])+
  labs(x = "", y = "Number of Images", fill = "")+
  scale_x_discrete(limits=c(unique(df_tot$CommonName)))+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 15,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 18))

```

##Mara Triangle Confidence >= 90%


```{r, echo = FALSE}

df_tot<-df_col%>%
  filter(MeanConf >=0.90,site_code == "MT")%>%
  group_by(CommonName)%>%
  mutate(freq = n())%>%
  ungroup()%>%
  arrange(desc(freq))


ggplot(df_tot, aes(x = CommonName))+
  geom_bar(fill = df_tot$cols[1])+
  labs(x = "", y = "Number of Imagesy", fill = "")+
  scale_x_discrete(limits=c(unique(df_tot$CommonName)))+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 15,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 18))


```

##Naboisho

```{r, echo = FALSE}

df_tot<-df_col%>%
  filter(site_code == "NB")%>%
  group_by(CommonName)%>%
  mutate(freq = n())%>%
  ungroup()%>%
  arrange(desc(freq))


ggplot(df_tot, aes(x = CommonName))+
  geom_bar(fill = df_tot$cols[1])+
  labs(x = "", y = "Number of Images", fill = "")+
  scale_x_discrete(limits=c(unique(df_tot$CommonName)))+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 15,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 18))

```

##Naboisho Confidence >= 90%

```{r, echo = FALSE}

df_tot<-df_col%>%
  filter(MeanConf >=0.90,site_code == "NB")%>%
  group_by(CommonName)%>%
  mutate(freq = n())%>%
  ungroup()%>%
  arrange(desc(freq))


ggplot(df_tot, aes(x = CommonName))+
  geom_bar(fill = df_tot$cols[1])+
  labs(x = "", y = "Number of Imagesy", fill = "")+
  scale_x_discrete(limits=c(unique(df_tot$CommonName)))+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 15,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 18))


```

##OMC

```{r, echo = FALSE}

df_tot<-df_col%>%
  filter(site_code == "OMC")%>%
  group_by(CommonName)%>%
  mutate(freq = n())%>%
  ungroup()%>%
  arrange(desc(freq))


ggplot(df_tot, aes(x = CommonName))+
  geom_bar(fill = df_tot$cols[1])+
  labs(x = "", y = "Number of Images", fill = "")+
  scale_x_discrete(limits=c(unique(df_tot$CommonName)))+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 15,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 18))

```

##OMC Confidence >= 90%

```{r, echo = FALSE}

df_tot<-df_col%>%
  filter(MeanConf >=0.90,site_code == "OMC")%>%
  group_by(CommonName)%>%
  mutate(freq = n())%>%
  ungroup()%>%
  arrange(desc(freq))


ggplot(df_tot, aes(x = CommonName))+
  geom_bar(fill = df_tot$cols[1])+
  labs(x = "", y = "Number of Imagesy", fill = "")+
  scale_x_discrete(limits=c(unique(df_tot$CommonName)))+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 15,angle =90, hjust = 1, vjust = 0.35),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.x = element_text(size = 18))

```



#Site based species counts

```{r, echo = FALSE}
SiteSpec<-df %>%
  filter(MeanConf >= 0.9)%>%
  dplyr::select(Site, CommonName)%>%
  distinct()%>%
  group_by(Site)%>%
  summarise(SpecFreq = n())

```

#Creating time series of effort for each conservancy
```{r, echo = FALSE}

exif_daily<-readRDS("daily_exif_counts.RDA")

site_daily_caps <- exif_daily %>%
                      group_by(Site.ID, date)%>%
                      summarise(daily_captures = sum(n))%>%
                      ungroup()


```


```{r, echo = FALSE}
site_daily_caps<-data.frame(site_daily_caps)

ef<-read.csv(here::here("effort/all_sites_effort.csv"), stringsAsFactors = FALSE)
ef$date<-as.Date(ef$date)

ef_cap<-merge(ef, site_daily_caps, by.x = c("date", "site"), by.y = c("date", "Site.ID"))

ef_cap$caps_per_ef <- ef_cap$daily_captures/ef_cap$effort 

ef_tot<-ef_cap

ef_tot$site<-"Total"

ef_tot<-ef_tot %>%
  group_by(date)%>%
  mutate(total_effort = sum(effort), total_captures = sum(daily_captures))%>%
  select(date,site, total_effort, total_captures)%>%
  distinct()%>%
  ungroup()

ef_tot$caps_per_ef<-ef_tot$total_captures/ef_tot$total_effort


colnames(ef_tot)<-colnames(ef_cap)

ef_all<-rbind(ef_tot, ef_cap)

ef_all$site_f = factor(ef_all$site, levels=c('Total','MT','OMC','NB', 'MN'))

site_labs<- c("Total", "Mara North", "Mara Triangle", "Naboisho", "OMC")
names(site_labs)<-c("Total", "MN", "MT", "NB", "OMC")
```


#Images/Effort over time

```{r, fig.width=18, fig.height=12}
ggplot(ef_all, aes(x = date, y  = caps_per_ef, group = site_f, colour = site_f))+
  geom_line(size =1.5)+
  #geom_point()+
  facet_grid(.~site_f, labeller = labeller(site_f = site_labs))+
  labs(x = "Date", y = "Number of Images\nper Camera Trap Day", colour = "Site")+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 20),
        strip.text.x = element_text(size = 18))

```


```{r, fig.width=18, fig.height=12}
ggplot(ef_all, aes(x = date, y  = caps_per_ef, group = site_f, fill = site_f))+
  geom_bar(width=1,stat = "identity")+
  facet_grid(.~site_f, labeller = labeller(site_f = site_labs))+
  labs(x = "Date", y = "Number of Images\nper Camera Trap Day", fill = "Site")+
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 20),
        strip.text.x = element_text(size = 14))



```